### 2025-07-04 index.qmd
20250704 - track chunk execution times

>>>>

```{r setup}
#| include: false

# Enable automatic chunk timing logging to GitHub Actions
knitr::opts_chunk$set(time = TRUE)  # Apply to ALL chunks globally

# Null coalescing operator
`%||%` <- function(a, b) if (!is.null(a)) a else b

# Define timing hook
knitr::knit_hooks$set(time = function(before, options) {
  if (before) {
    options$start_time <- Sys.time()
  } else {
    elapsed <- difftime(Sys.time(), options$start_time, units = "secs")
    msg <- sprintf("::notice title=Chunk Time::Chunk `%s` ran in %.2f seconds.", 
                   options$label %||% "<unnamed>", as.numeric(elapsed))
    message(msg)  # Send to GitHub Actions log
  }
})
```
